---
title: "london_visits"
author: "Elvis Leng"
date: "9/13/2018"
output: html_document
---
```{r}

library(readxl)
library(dplyr)
library(plotly)
library(ggplot2)
library(heplots)
library(reshape)
library(ggcorrplot)
library("Hmisc")
library(tidyverse)
library(ggthemes)

for (x in excel_sheets('PI_All_data_2007-2017.xlsx')){
  name <- paste('all', x, sep = '_')
  assign(name, read_excel('PI_All_data_2007-2017.xlsx',sheet = x))
}

for (x in excel_sheets('international-visitors-london.xls')){
  name <- paste('iv', x, sep = '_')
  assign(name, read_excel('international-visitors-london.xls',sheet = x))
}
```

```{r}
#as year progresses, yearly visits generally goes up with a decrease in 2016. Year spend also goes up as year progresses.

ggplotly(ggplot(`iv_Raw data` %>% group_by(year) %>% summarise(spendAmount = sum(spend),year_visit = sum(visits)), aes(x = year, y = year_visit, size = spendAmount, color = spendAmount))+geom_point()+theme_economist()+ labs(title ='Total Money Spent and Amount of Visitors', x = 'Year', y = 'Total Amount of Visits')+scale_fill_discrete(name="Spending Amount"))

```


```{r}
ggplotly(ggplot(`iv_Raw data` %>% group_by(year) %>% summarise(avg_nights = mean(nights), total_spend = sum(spend)), aes(x = year, y = avg_nights, size = total_spend, color = total_spend))+geom_point()+theme_economist() + labs(title = 'Average Nights Spent and Money Spent', x = 'Year', y = 'Average Nights')+scale_fill_discrete(name="Total Spending"))
```



```{r}
ggplotly(ggplot(`iv_Raw data` %>% group_by(year, quarter) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend,  fill = quarter) )+ geom_bar(stat = "identity", width = 0.8, position=position_dodge())+theme_economist() + labs(title = 'Total Spend by Quarter and Year', x= 'Year', y = 'Total Spend', legend = 'Quarter')+scale_fill_discrete(name="Quarter")+scale_fill_discrete(name="Quarter")) 

```
As you can see from the above, quarter 3's spend is consisitantly above all the other quarters. 





```{r}
plot_ly(`iv_Raw data` %>% group_by(mode) %>% summarise(total_spend = sum(spend)), labels = ~mode, values = ~total_spend, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>% layout(title = 'Total Spend by Different Transportation Methods', showlegend = T)


```


As you can see from here, people travel via air spend the most amount of money. 

```{r}
ggplotly(ggplot(`iv_Raw data` %>% group_by(year, mode) %>% summarise(total_spend = mean(spend)), aes(x = year , y = total_spend,  fill = mode) )+ geom_bar(stat = "identity", width = 0.8, position=position_dodge())+theme_economist()+labs(title ='Average Money Spent By Different Transportation Modes', x= 'Year', y = 'Average Money Spent') +scale_fill_discrete(name="Traffic"))
```

As you can see, people travel via Tunnel and Air are increasing the money the spent on average, but people travel via sea have a constant spend rate. 

```{r}
plot_ly(`iv_Raw data` %>% group_by(purpose) %>% summarise(total_spend = round(sum(spend),2)), labels = ~purpose, values = ~total_spend, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>% layout(title = 'Total Spent by Different Travel Purposes', showlegend = T)

```
As we can see from above, people come here for holiday spend the most amount of money


```{r}
plot_ly(`iv_Raw data` %>% group_by(market) %>% summarise(total_spend = round(sum(spend),2)), labels = ~market, values = ~total_spend, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>%  layout(title = "Country and the Amount of Money Spent",  showlegend = T)

```
```{r}
plot_ly(`iv_Raw data` %>% group_by(market) %>% summarise(total_spend = round(mean(spend),2)), labels = ~market, values = ~total_spend, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>%  layout(title = "Country and the Average Amount of Money Spent",  showlegend = T)

```



```{r}
ggplotly(ggplot(all_busi_var %>% subset(country =='United States' | country == 'France'| country =='Germany'| country == 'Italy'| country =='Spain'), aes(x = year, y = busi,  fill = country) )+ geom_bar(stat = "identity", width = 0.8, position=position_dodge())+theme_economist() + labs(title = "Top 5 Most Spent Countries Busi Ranking" )+scale_fill_discrete(name="Country")) 

```
for the top five spending countries, I looked at their economic scale. United states has the highest scale, and they are spending the most amount of money. 


show country's spending trend 


```{r}

ggplotly(ggplot(`iv_Raw data` %>% subset(market == "Italy") %>% group_by(year) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend) )+geom_point() + geom_smooth(method = "lm")+theme_economist() +labs(title = 'Spending Trend of Italy', x = 'Year', y = 'Total Spend'))

```





```{r}

ggplotly(ggplot(`iv_Raw data` %>% subset(market == "Spain") %>% group_by(year) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend) )+geom_point() + geom_smooth(method = "lm")+theme_economist() +labs(title = 'Spending Trend of Spain', x = 'Year', y = 'Total Spend'))

```
```{r}

ggplotly(ggplot(`iv_Raw data` %>% subset(market == "Kuwait") %>% group_by(year) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend) )+geom_point() + geom_smooth(method = "lm")+theme_economist() +labs(title = 'Spending Trend of Kuwait', x = 'Year', y = 'Total Spend'))

```
```{r}

ggplotly(ggplot(`iv_Raw data`%>% subset(market == "Saudi Arabia") %>% group_by(year) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend) )+geom_point() + geom_smooth(method = "lm")+theme_economist() +labs(title = 'Spending Trend of Saudi Arabia', x = 'Year', y = 'Total Spend'))

```


```{r}

ggplotly(ggplot(`iv_Raw data` %>% subset(market == "Australia") %>% group_by(year) %>% summarise(total_spend = sum(spend)), aes(x = year, y = total_spend) )+geom_point() + geom_smooth(method = "lm")+theme_economist() +labs(title = 'Spending Trend of Australia', x = 'Year', y = 'Total Spend'))

```
```{r}
plot_ly(`iv_Raw data` %>% subset(dur_stay== '15+  nights') %>% mutate(count = 1) %>% group_by(market) %>% summarise(total_count = sum(count)), labels = ~market, values = ~total_count, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>% layout(showlegend = T, title = 'Percentage of Countries who Stay Over 15 Days')

```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+theme_economist() +geom_smooth(method = 'lm') +labs(title = 'General Trend of People Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```





```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'USA') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm')+theme_economist()  +labs(title = 'Trend of People From USA who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))

```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'France') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From France who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))

```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Australia') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Australia who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'China') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From China who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Kuwait') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Kuwait who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Mexico') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Mexico who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Taiwan') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Taiwan who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```
```{r}
summary(lm(total_count~year, data = `iv_Raw data` %>% subset(market =='Taiwan') %>% mutate( count = 1) %>% group_by(year) %>% summarise(total_count = sum(count))))
etasq(lm(total_count~year, data = `iv_Raw data` %>% subset(market =='Taiwan') %>% mutate( count = 1) %>% group_by(year) %>% summarise(total_count = sum(count))), anova= TRUE, partial= FALSE)
```

```{r}
for (x in excel_sheets('international-visitors-london.xls')){
  name <- paste('iv', x, sep = '_')
  assign(name, read_excel('international-visitors-london.xls',sheet = x))
}
```
-----------------------------------------------------
Duration over 15 days 
```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Kuwait') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Kuwait who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Mexico') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Mexico who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Taiwan') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Taiwan who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
summary(lm(total_count~year, data = `iv_Raw data` %>% subset(market =='Taiwan') %>% mutate( count = 1) %>% group_by(year) %>% summarise(total_count = sum(count))))
etasq(lm(total_count~year, data = `iv_Raw data` %>% subset(market =='Taiwan') %>% mutate( count = 1) %>% group_by(year) %>% summarise(total_count = sum(count))), anova= TRUE, partial= FALSE)
```
Below we are only going to focus on the countries that spend more than 15 nights in London
```{r}
plot_ly(`iv_Raw data` %>% subset( dur_stay == '15+  nights') %>% group_by(market) %>% summarise(total_spend = round(mean(spend),2)), labels = ~market, values = ~total_spend, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>%  layout(title = "Country and the Average Spending For 15+ Days Duration",  showlegend = T)

```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Qatar') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Qatar who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Saudi Arabia') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Saudi Arabia who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Australia') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Australia who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Oman') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Oman who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'United Arab Emirates') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From United Arab Emirates who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% subset(dur_stay== '15+  nights' & market == 'Nigeria') %>% mutate(count =1) %>% group_by(year) %>% summarise(total_count = sum(count)), aes(x = year, y = total_count))+geom_point()+geom_smooth(method = 'lm') +theme_economist() +labs(title = 'Trend of People From Nigeria who Stay Over 15+ Days', x = 'Year', y = 'Total Visit'))
```

```{r}
eu_nation <- c('Austria', 'Belgium', 'Bulgaria', 'Croatia', 'Cyprus', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Irish Republic', 'Italy', 'Latvia', 'Lithuania', 'Luxembourg', 'Malata', 'Netherlands', 'Poland', 'Portugal', 'Romania', 'Slovakia', 'Slovenia', 'Spain', 'Sweden')
```


```{r}
ggplotly(ggplot(`iv_Raw data` %>% mutate(EU = ifelse(market %in%eu_nation, 'EU', 'NON-EU')) %>% group_by(EU,year) %>% summarise(total = sum(visits)), aes(y=total, x = year, color = EU))+geom_point()+geom_line()+theme_economist()+labs(x = 'Year', y = 'Total Visits', title ='EU Total Visits Compare to Non-EU Total Visits'))
```


```{r}
plot_ly(`iv_Raw data` %>% group_by(dur_stay) %>% summarise(total_visits = sum(visits)), labels = ~dur_stay, values = ~total_visits, type = 'pie',textposition = 'inside',textinfo = 'label+percent+value') %>% layout(title = 'Total Visits by Different Nights', showlegend = T)
```

```{r}
ggplotly(ggplot(`iv_Raw data` %>% group_by(year, dur_stay) %>% summarise(total_spend = sum(visits)), aes(x = year, y = total_spend,fill = dur_stay) )+ geom_bar(stat = "identity", width = 0.9, position=position_dodge())+ theme_economist()+scale_fill_discrete(name="Duration Stay")+labs(title = 'Total Visits by Different Duration', x= 'Year', y = 'Total Visits'))
```


Time Series
```{r}

ivduration15<-`iv_By duration`[,c(1,5,6,10,11,15,16,20,21)]
colnames(ivduration15)<-c("Year/Nights", "Visits (15+ Nights/Year)","Total Visits",
                          "Nights (15+ Nights/Year)","Total Nights","Spending (15+ Nights/Year)",
                          "Total Spending", "Sample Size 15+","Total Sample")
ivduration15<-ivduration15[-1,]

#convert Column 1 to index
#as.data.frame(ivduration15)
#as.data.frame(ivduration15[,-1], row.names = ivduration15[,1])
#ivduration15 %>% remove_rownames %>% column_to_rownames(var="Year/Nights")
#ivduration15 <- ivduration15[-1]

#convert column to row names
ivduration15=as.matrix(ivduration15)
row.names(ivduration15)=as.numeric(ivduration15[,1])
ivduration15<-ivduration15[,-1]

#Time Series Plot
ts.plot(ivduration15,gpars= list(col=rainbow(8)))
legend("topleft", legend = colnames(ivduration15), col = 2:9, lty = 10)


```


```{r}
dur15<-ivduration15[,c(1,3,5)]
ts.plot(dur15,gpars= list(col=rainbow(3)))
legend("topleft", legend = colnames(dur15), col = 1:5, lty = 1)

```

```{r}
#Get a table that contains the countries and the number of visits by year
countryvis<-`iv_By country`[1:17]
countryvis<-countryvis[-1,]
colnames(countryvis)<-c("Country of Origin Visits","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015","2016","2017" )
countryvisnototal<-countryvis[-c(63),]
```


```{r}

#flip the columns and rows

countryvisnew<-data.frame(t(countryvis))
colnames(countryvisnew)<-as.character(unlist(countryvisnew[1,]))
countryvisnew<-countryvisnew[-1,]
#countryvisnew <- cbind(Row.Names = rownames(countryvisnew), countryvisnew)
#rownames(countryvisnew) <- NULL
```

```{r}
#plot time series data total visits by country
ts.plot(countryvisnototal,gpars= list(col=rainbow(12)))
legend("topleft", legend = colnames(ivduration15), col = 2:9, lty = 1)
      
```


Correlation
```{r}
str(`iv_Raw data`)

dfList <- list(all_busi,all_econ, all_educ,all_envi,all_gove,all_heal,all_pers,all_Prosperity,all_safe,all_soci)

newlist<-lapply(dfList, function(df) {
  #Drop rank columns since rank doesn't provide sufficient info on correlation
  newdf<-df %>% select(-contains("rank"))
  #Reshape Data since years of two dataset are not in the same dimension
  newdf<-newdf %>% as.data.frame %>% melt(., id = c("country","isonum","isocode","region","region2")) 
  #Remove strings before 4 digit year
  newdf$variable<-gsub("[a-zA-Z]|_", "", newdf$variable) 
  return(newdf)
})
#assign df names
busi<-as.data.frame(newlist[1])
econ<-as.data.frame(newlist[2])
educ<-as.data.frame(newlist[3])
envi<-as.data.frame(newlist[4])
gove<-as.data.frame(newlist[5])
heal<-as.data.frame(newlist[6])
pers<-as.data.frame(newlist[7])
Prosperity<-as.data.frame(newlist[8])
safe<-as.data.frame(newlist[9])
soci<-as.data.frame(newlist[10])

#Change columns to classify for further merge steps
colnames(busi)[which(names(busi) == "value")] <- "busi"
colnames(econ)[which(names(econ) == "value")] <- "econ"
colnames(educ)[which(names(educ) == "value")] <- "educ"
colnames(envi)[which(names(envi) == "value")] <- "envi"
colnames(gove)[which(names(gove) == "value")] <- "gove"
colnames(heal)[which(names(heal) == "value")] <- "heal"
colnames(pers)[which(names(pers) == "value")] <- "pers"
colnames(Prosperity)[which(names(Prosperity) == "value")] <- "Prosperity"
colnames(safe)[which(names(safe) == "value")] <- "safe"
colnames(soci)[which(names(soci) == "value")] <- "soci"

merge1<-merge(x = `iv_Raw data`, y = busi, by.x = c("market","year"), by.y = c("country","variable"))
merge2<-merge(merge1, econ, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
#CHECK 
#merge2[which(merge2$isonum == "32"), ]
merge3<-merge(merge2, educ, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge4<-merge(merge3, envi, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge5<-merge(merge4, gove, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge6<-merge(merge5, heal, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge7<-merge(merge6, pers, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge8<-merge(merge7, Prosperity, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge9<-merge(merge8, safe, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
merge10<-merge(merge9, soci, by.x = c("market","isonum","isocode","region","region2","year"), by.y = c("country","isonum","isocode","region","region2","variable"))
str(merge10)
df<- merge10[, !(colnames(merge10) %in% c("market", "isonum","isocode","region","region2","quarter","dur_stay","mode","purpose","area"))]
#df$year<-as.numeric(df$year)
str(df)
corr<-cor(df)
corr
#plot the correlation matrix visual
#You can see a moderate to strong correlation between prosperity and gove/education/econ/busi
ggcorrplot(corr,lab = TRUE)
corr2<-as.matrix(df)
corr3<-rcorr(corr2, type = c("pearson","spearman"))
str(corr3)
#r : the correlation matrix
#n : the matrix of the number of observations used in analyzing each pair of variables
#P : the p-values corresponding to the significance levels of correlations.
# p-values
a<-corr3$P
a
```

```{r}
quarterlm1<-lm(`iv_By quarter`$`Total Visits (000s)`~`iv_By quarter`$Year + `iv_By quarter`$Quarter + `iv_By quarter`$`Total Nights (000s)` + `iv_By quarter`$`Total Spend (£m)` + `iv_By quarter`$`Sample size`)
summary(quarterlm1)
```

```{r}
vif(quarterlm1)
plot(quarterlm1)
```

```{r}
quarterlm2<-lm(`iv_By quarter`$`Total Visits (000s)`~ `iv_By quarter`$Quarter + `iv_By quarter`$`Total Nights (000s)` + `iv_By quarter`$`Total Spend (£m)` + `iv_By quarter`$`Sample size`)
summary(quarterlm2)
```
```{r}
vif(quarterlm2)
plot(quarterlm2)
```

```{r}
quarterlm3<-lm(`iv_By quarter`$`Total Visits (000s)`~ `iv_By quarter`$Quarter + `iv_By quarter`$`Total Spend (£m)` + `iv_By quarter`$`Sample size`)
summary(quarterlm3)
```
```{r}
vif(quarterlm3)
plot(quarterlm3)
```



